---
title: "Linear Model"
author: "Taylor Stohl"
date: "6/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```







## Including Plots

You can also embed plots, for example:



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

###Plot scatterplot



```{r}
plot(SIMS~ARM,data=data)
```
##Now with ggplot - first select the basic data



```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```
  
  


The y-axis is SIMS and the x-axis is ARM. This plot shows that there is a positive linear correlation. 


# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The value is 0.68, which is a positive number that indicates the line will travel upwards towards the right.




# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The evaluation for the line that fits this is SIMS is equal to -4.1 + .05 * ARM
The formula needed is y = mx + b to create a line. The Adjusted R-squared is the number to look at


# now add the model fit to our plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

It looks like the value of the Y-intercept would be around 1.







